---
title: "Toy Problems Example"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---

```{r, include = F}
library(tidyverse)
```
## Introduction

This document details the procedure to run the oblique BART and axis-aligned BART rotated axes and sin wave experiments.

## Settings

Below, we load the settings for the toy experiments. The specific files to do so are located in the study folder for 'toy_examples'.

```{r}
source("study/settings.R")
head(settings)
```

Each row in the settings dataframe represents the parameters of a single run of the experiments. There are 3 different models. The first is *obart7*, which is the default implementation of obliqueBART. We compare obliqueBART with *awbart*, the standard implementation of axis-aligned BART, and *rwbart*, which is axis-aligned BART with the rotated features.
The dataframe also contains the experiment type, which is represented by the variable "exp". The two experiments are the sin wave and rotated axes experiments, described in section XXX of XXX.
Finally, "p" denotes the number of random rotations used in *rwbart*.   


The script study.R takes as input a row index (job_id) and runs the corresponding method on a training-testing split for the corresponding method.

To run the experiment for a single row job_id locally, you should comment out the lines

```{r}
args <- commandArgs(TRUE)
job_id <- as.numeric(args[1])
```


and instead manually set job_id (around line 8 of the script)

After running the experiment for all rows, you can tabulate and graph the results by running the analyze_results.R script.